\documentclass{ctuthesis}

\usepackage{wrapfig}
\usepackage{array,multirow}
\usepackage{subcaption}
\usepackage{cite}
\usepackage{listings}
\usepackage{svg}
\usepackage{hyperref}
\usepackage{makecell}
\usepackage{cleveref}
\usepackage{dirtree}
\usepackage{enumitem}
\renewcommand\theadalign{bc}
\renewcommand\theadfont{\bfseries}
\renewcommand\theadgape{\Gape[4pt]}
\renewcommand\cellgape{\Gape[4pt]}
\renewcommand{\cref}[1]{\Cref{#1}}
\renewcommand{\crefrange}[1]{\Crefrange{#1}}

\def\UrlBreaks{\do\/\do-}
\usepackage{breakurl}


\providecommand{\e}[1]{\ensuremath{\times 10^{#1}}}


\ctusetup{
    xdoctype = M,
    xfaculty = F3,
    mainlanguage = english,
    titlelanguage = english,
    title-english = {Long-term person re-identification in video},
    title-czech = {Transfer learning pro klasifikaci textu},
    department-english = {Department of Cybernetics},
    author = {Martina Tichá},
    supervisor = {Ing. Jiří Čermák, Ph.D.},
    supervisor-address = {Blindspot Solutions, Praha},
    fieldofstudy-english = {Open Informatics},
	subfieldofstudy-english = {Computer vision and digital image processing},
	day = 24,
    month = 5,
    year = 2019,
    specification-file = {zadani.pdf}, 
    front-specification = true,
	keywords-czech = {zpracování přirozeného jazyka, klasifikace textu, umělá neuronová síť, strojové učení},
	keywords-english = {natural language processing, text classification, artificial neural network, machine learning, transfer learning}
}

\ctuprocess

\begin{abstract-english}
The recent developments of Language Modeling led to advances in transfer learning methods in Natural Language Processing. Language Models pretrained on large general datasets achieved state-of-the-art results in a wide range of tasks. The \textit{Universal Language Model Fine-tuning} represents an effective transfer learning method for text classification. The goal of this thesis is to further test the robustness of this method in scenarios, commonly found in real-world applications. 

\end{abstract-english}

\begin{abstract-czech}
Nedávné vývoje v jazykových modelech vedly k posunu v transfer learning metodách ve zpracování přirozeného jazyka. Jazykové modely předtrénované na rozsáhlých obecných datasetech dosahují nejlepších výsledků v celé řadě úkolů. \textit{Universal Language Model Fine-tuning} představuje efektivní transfer learning metodu pro klasifikaci texu. Cílem této práce je hlouběji otestovat robustnost této metody ve scénářích, které se běžně nacházejí při reálných aplikacích.
\end{abstract-czech}

\begin{thanks}
Most of all, I would like to thank my supervisor, Jiří Čermák, who guided me throughout writing this thesis as well as to Štěpán Kopřiva and all the great people at Blindspot.ai.

I am grateful to all my friends and family: my parents and grandparents, my sister, and my wonderful girlfriend for always supporting me.

Finally, I want to thank the following coffee roasters, which provided  me with the much-needed fuel: Pražírna, doubleshot, KK, Dos Mundos, and Coffee Source.
\end{thanks}


\begin{declaration}
I declare that the presented work was developed independently and that I have listed all sources of information used within it in accordance with the methodical instructions for observing the ethical principles in the preparation of the university theses.
\\
\\
\\
\makebox[0.8\columnwidth]{\dotfill}
\\
Pavel Janata \\
Prague, \ctufield{day}th~\monthinlanguage{title}~\ctufield{year}
\end{declaration}


\begin{document}

\maketitle

\input{chapters/1_introduction}
\input{chapters/2_related_works.tex}
\input{chapters/3_technical_background.tex}
\input{chapters/4_gait_recognition.tex}
\input{chapters/5_data_sets.tex}
\input{chapters/6_proposed_solutions.tex}
\input{chapters/7_results.tex}
\input{chapters/8_future_work.tex}
\input{chapters/9_conclusion.tex}
% \input{chapters/10_appendices.tex}

\appendix



\bibliographystyle{plain}
\bibliography{bibliography}


\end{document}